Syntax and Semantics of Abstract Binding Trees

### 2015-12-06 paper.tex
layout
use copresheaf
ehh, I changed my mind.

Intuitively, when $\Upsilon$ supports $\Member{m}{X(\Upsilon')}$, we would
expect that we can work backward to a unique $\Of{m'}{\Upsilon}$ such that
$\IsEq{m'\cdot\varrho}{m}$; whilst it is not in general the case for presheaves
$X$, this is precisely the sheaf condition for covariant presheaves on $\SCtx$
under the atomic topology \cite[p.~126]{mac-lane-moerdijk:1992}. The sheaf
condition, then, ensures that the notion of support is well-behaved.

@@

\begin{gather*}
  \infer[\textit{var}]{
    \IsAbt{\Theta}{\Upsilon}{\Gamma}{x}{\tau}
  }{
    \Lookup{\Gamma}{x}{\tau}
  }
\\[6pt]
  \infer[\textit{mvar}]{
    \IsAbt{\Theta}{\Upsilon}{\Gamma}{
      \MApp{\MV{m}}{u_0,\dots,u_m}{M_0,\dots,M_n}
    }{\tau}
  }{
    \begin{array}{l}
      \Lookup{\Theta}{\MV{m}}{
        \MkValence{
          \sigma_0,\dots,\sigma_m
        }{
          \tau_0,\dots,\tau_n
        }{\tau}
      }
\\
      \HypJ{
        \Lookup{\Upsilon}{u_i}{\sigma_i}
      }{\Leq{i}{m}}
\\
      \HypJ{
        \IsAbt{\Theta}{\Upsilon}{\Gamma}{M_i}{\tau_i}
      }{\Leq{i}{n}}
    \end{array}
  }
\\[6pt]
  \infer[\textit{app}]{
    \IsAbt{\Theta}{\Upsilon}{\Gamma}{
      \App{\vartheta}{E_0,\dots,E_n}
    }{\tau}
  }{
    \begin{array}{l}
      \IsOperator{\Upsilon}{\vartheta}{
        \MkArity{v_1,\dots,v_n}{\tau}
      }
\\
      \HypJ{
        \IsBTm{\Theta}{\Upsilon}{\Gamma}{E_i}{v_i}
      }{\Leq{i}{n}}
    \end{array}
  }
\\[6pt]
  \infer[\textit{abs}]{
    \IsBTm{\Theta}{\Upsilon}{\Gamma}{
      \MkBTm{\vec{u}}{\vec{x}}{M}
    }{
      \MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}
    }
  }{
    \IsAbt{
      \Theta
    }{
      \Upsilon, \vec{u}:\vec{\sigma}
    }{
      \Gamma,\vec{x}:{\vec{\tau}}
    }{
      M
    }{\tau}
  }
\end{gather*}

>>>>

Intuitively, when $\Upsilon$ supports $\Member{m}{X(\Upsilon')}$, we would
expect that we can work backward to a unique $\Of{m'}{\Upsilon}$ such that
$\IsEq{m'\cdot\varrho}{m}$; whilst it is not in general the case for presheaves
$X$, this is precisely the sheaf condition for copresheaves on $\SCtx$
under the atomic topology \cite[p.~126]{mac-lane-moerdijk:1992}. The sheaf
condition, then, ensures that the notion of support is well-behaved.

@@

\[
  \infer[\textit{var}]{
    \IsAbt{\Theta}{\Upsilon}{\Gamma}{x}{\tau}
  }{
    \Lookup{\Gamma}{x}{\tau}
  }
\]
\[
  \infer[\textit{mvar}]{
    \IsAbt{\Theta}{\Upsilon}{\Gamma}{
      \MApp{\MV{m}}{u_0,\dots,u_m}{M_0,\dots,M_n}
    }{\tau}
  }{
    \begin{array}{l}
      \Lookup{\Theta}{\MV{m}}{
        \MkValence{
          \sigma_0,\dots,\sigma_m
        }{
          \tau_0,\dots,\tau_n
        }{\tau}
      }
\\
      \HypJ{
        \Lookup{\Upsilon}{u_i}{\sigma_i}
      }{\Leq{i}{m}}
\\
      \HypJ{
        \IsAbt{\Theta}{\Upsilon}{\Gamma}{M_i}{\tau_i}
      }{\Leq{i}{n}}
    \end{array}
  }
\]
\[
  \infer[\textit{app}]{
    \IsAbt{\Theta}{\Upsilon}{\Gamma}{
      \App{\vartheta}{E_0,\dots,E_n}
    }{\tau}
  }{
    \begin{array}{l}
      \IsOperator{\Upsilon}{\vartheta}{
        \MkArity{v_1,\dots,v_n}{\tau}
      }
\\
      \HypJ{
        \IsBTm{\Theta}{\Upsilon}{\Gamma}{E_i}{v_i}
      }{\Leq{i}{n}}
    \end{array}
  }
\]
\[
  \infer[\textit{abs}]{
    \IsBTm{\Theta}{\Upsilon}{\Gamma}{
      \MkBTm{\vec{u}}{\vec{x}}{M}
    }{
      \MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}
    }
  }{
    \IsAbt{
      \Theta
    }{
      \Upsilon, \vec{u}:\vec{\sigma}
    }{
      \Gamma,\vec{x}:{\vec{\tau}}
    }{
      M
    }{\tau}
  }
\]
